\subsection{Materials}
\begin{itemize}
	\item Combined amplifier, filter and driving circuit
	\item Function generator and oscilloscope. NI myDAQ used for both.
	\item Phosphate buffer solution (PBS)
	\item Activated yeast (\textit{Saccharomyces cerevisiae})
\end{itemize}

\subsection{Methods}
\begin{enumerate}
	\item 
\end{enumerate}
\paragraph{Variables}
\begin{itemize}
	\item Control:
		\begin{itemize}
			\item Output voltage on function generator: 10V.
			\item Probes 180ยบ from each other. Sense leads 30ยบ from the probe and 180ยบ from each other. See Figure \ref{fig:ElectrodeOrientation}.
			\item Amplifier gain $\frac{15k}{150} = 100$.
			\item Liquid volume 250 ml, 60mm height measured from inside the cup.
		\end{itemize}
	\item Independent: Frequency.
	\item Dependent: Potential difference
\end{itemize}
\begin{figure}[h]
	\newcommand{\Radius}{3}
	\newcommand{\RadPow}{0.5}
	\newcommand{\RadVolt}{0.5}
	\centering
	\begin{circuitikz}[scale=0.75]
		\draw (0,0) circle (\Radius cm);
		%Driving electrodes
		\draw [dashed,cyan] (0,-\Radius) node{*} -- (0,\Radius) node{*};
		\node at (0.3,-\Radius-0.3) {-$V_x$};
		\node at (0.3,\Radius+0.3) {$V_x$};
		\draw [cyan] (0,\Radius) -- ++ (0,\RadPow)
			-- ++ ({-\Radius*1.3},0)
			-- ++ (0,{-\Radius}) 
			++ (0,0) to[vsourcesin,a=\SI{10}{\volt},color=cyan] ++ (0,-2*\RadPow)
			-- ++ (0,{-\Radius})
			-- ++ ({\Radius*1.3},0)
			-- ++ (0,{\RadPow})
		;
		% Sensor electrodes
		\draw[dashed, red] ({\Radius*cos(60)},{-\Radius*sin(60)}) node{*} -- ({-\Radius*cos(60)},{\Radius*sin(60)}) node{*} coordinate (a);
		\draw [red]
			(a) -- ++ (-{(2*\RadVolt*0.8)*cos(60)}, {(2*\RadVolt*0.8)*sin(60)}) coordinate (a)
			-- ++ (0,0) arc (-60:120:0.2)
			-- ++ ({1.3*\Radius*cos(30)},{1.3*\Radius*sin(30)})
			-- ++ ({(\Radius+\RadVolt)*cos(60)},{-(\Radius+\RadVolt)*sin(60)})
			++ ({\RadVolt*cos(60)},{-\RadVolt*sin(60)}) circle (\RadVolt) node{V} ++ ({\RadVolt*cos(60)},{-\RadVolt*sin(60)})
			-- ++ ({(\Radius+\RadVolt)*cos(60)},{-(\Radius+\RadVolt)*sin(60)})
			-- ++ ({-1.3*\Radius*cos(30)},-{1.3*\Radius*sin(30)})
			-- ++ ({(-2*\RadVolt*0.8)*cos(60)}, {(2*\RadVolt*0.8)*sin(60)})
		;
		%
		\draw [<->] (0,\Radius*0.5) arc (90:120:\Radius*0.5) node[pos=0.5,anchor=south]{30ยบ};
		\matrix [draw, matrix of math nodes] at (current bounding box.north east) {
    		 \color{cyan}* & \text{Driving electrodes} \\
			 \color{red}* & \text{Sensing electrodes} \\
	 	};
	\end{circuitikz}
	\caption{Orientation of electrodes}
	\label{fig:ElectrodeOrientation}
\end{figure}

\paragraph{Considerations}

Due to a limited power input into the amplifier, a gain ratio of 1000 led to \textit{gain saturation}, where we no longer observed the expected amplification.
With gain of 10, the maxima appeared in different frequencies as to those of 100 and 1000, though we are unsure why this would happen.

Although we defined probe orientation, there are two factors we are disregarding: the cup is not perfectly cylindrical, and the leads are not straight -- so the distance between electrodes is smaller than what the experimental setup implies.
Instrumental uncertainty becomes largely irrelevant, as we expect there to be some movement in the probes as we  

Maximum amplitude for PBS around 3000hz, maximum amplitude for yeast at 5000hz. We pick 4000 Hz.
There is no concern for cell disruption at the range of frequencies we are analysing (Yerworth, R., 2019 November 28)